Introduction

### 2025-01-27 intro.qmd
Various minor improvements
Minor improvements

Suppose you are reading an article about a new imaging method to turn seismological data into subsurface images. The article describes the ideas that went into developing this method and presents a few examples to illustrate its superiority over previous approaches. You got interested and would like to apply this method to your own data. However, with only the article available, it could take months to come up with a working solution, if possible at all. This situation has been put aptly by Buckheit & Donoho [-@Buckheit1995, p. 59], distilling an idea by the geophysicist Jon Claerbout:

@@

However, there's more to code publishing than sharing. Researchers should document (i.e., track) which data, software, images, texts, and other materials contributed to their work. In more elaborate terms, researchers should preserve the _provenance_ of shared materials, for at least three tangible reasons:

>>>>

Suppose you are reading an article about a new imaging method to turn seismological data into subsurface images. The article describes the ideas that went into developing this method and presents a few examples to illustrate its superiority over previous approaches. You got interested and would like to apply this method to your own data. However, with only the article available, it could take you months to come up with a working solution, if possible at all. This situation has been put aptly by Buckheit & Donoho [-@Buckheit1995, p. 59, emphasis in original], distilling an idea by the geophysicist Jon Claerbout:

@@

However, there's more to code publishing than sharing. Researchers should document (i.e., track) which foreign data, software, images, texts, and other materials contributed to their work. In more elaborate terms, researchers should preserve the _provenance_ of shared materials, for at least three tangible reasons:
